The Astropy Project

### 2017-10-20 main.tex
Update on Overleaf.

Several classes are provided for determining intervals and for normalizing values in this interval to the [0:1] range.
In addition, classes are provided in order to identify lower and upper limits for a dataset based on specific algorithms (such as using percentiles).

@@

>>>>

Several classes are provided for determining intervals (e.g. using image percentiles) and for normalizing values in this interval to the [0:1] range.

\package{Matplotlib} allows a custom normalization and stretch to be used when displaying data by passing a normalization object.  The \package{visualization} package also provides a normalization class that wraps the interval and stretching objects into a normalization object that \package{matplotlib} understands.

@@

Lupton et al. (2004) describe an “optimal” algorithm for producing red-green- blue composite images from three separate high-dynamic range arrays. This method is implemented in make_lupton_rgb as a convenience wraper function and an associated set of classes to provide alternate scalings. The SDSS SkyServer color images were made using a variation on this technique.
